Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
commented out paragraph about internal observer

\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}

\todo{[The remainder of the section needs to be updated. ]}
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
\todo{[Unclear what the remainder is for: ]}

>>>>

% \todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}

% \todo{[The remainder of the section needs to be updated. ]}
% The output and measurable of the plant is being sampled by an ADC, and since the full state of the
% plant cannot be witnessed directly, the controller software includes an observer that 
% estimates the state of the plant (see appendix for details on how such an observer
% is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
% \todo{[Unclear what the remainder is for: ]}
